Delayed effects of [responses to?] climate lead to demographic divergence in a fragmented Amazonian landscape

### 2021-03-24 doc/paper.Rmd
edded refs to discussion
fixed up a few citations

-   @dowd (unpublished thesis, could write MB and ask for update): precipitation and fragmentations influenced fruit/seed production by Heliconia (one step past flaowering, so might be worth citing to say that there are other ways reprod. can be affected

-   Lots of great stuff about the importance of rhizomes, including for drought resistance, in @klimeová2018. Rhizome resistance to variability in environmental conditions also a conclusion in this study on invasion by another zingiberales ( @pinheiro2021

@@

-   the observed effects on reproduction can have effects beyond demography, eg.
    gene flow and genetic structure among and between plots already shaped by fragmentation ( @cortes2013, there can also be drought effects eg @sifres2006)

@@

-   @rundel1998 Heliconia appear to allocate much of their above-ground biomass to leaf tissues and have a relatively low investment in support tissues.
    Investment in leaf form vs structure interpreted as a trade-off between economy and protection against tissue loss from falling branches; presence of below-ground rhizomes in Heliconia may be key.
    See also @rundel2020 \

@@

We thank ----, ----, ----, and --- anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. ---- in the BDFFP Technical Series.

>>>>

-   @dowd2020 (unpublished thesis, could write MB and ask for update): precipitation and fragmentations influenced fruit/seed production by Heliconia (one step past flaowering, so might be worth citing to say that there are other ways reprod. can be affected

-   Lots of great stuff about the importance of rhizomes, including for drought resistance, in @klimesova2018.
    Rhizome resistance to variability in environmental conditions also a conclusion in this study on invasion by another zingiberales ( @pinheiro2021

@@

-   the observed effects on reproduction can have effects beyond demography, eg.
    gene flow and genetic structure among and between plots already shaped by fragmentation ( @cortes2013, there can also be drought effects eg @sifres2007)

@@

-   @rundel1998 Heliconia appear to allocate much of their above-ground biomass to leaf tissues and have a relatively low investment in support tissues.
    Investment in leaf form vs structure interpreted as a trade-off between economy and protection against tissue loss from falling branches; presence of below-ground rhizomes in Heliconia may be key.
    See also @rundel2020\

@@

We thank ----, ----, ----, and --- anonymous reviewers for helpful discussions and comments on the manuscript.
We also thank the technicians and students who helped conduct the *Heliconia* censuses and the BDFFP and INPA for logistical support.
Financial support was provided by the U.S.
National Science Foundation (awards DEB-0614339, DEB-0614149, INT 98-06351, and DEB-1948607).
This is publication No. ------ in the BDFFP Technical Series.
